Verifying Demonstrations

### 2018-10-31 paper/system-model.tex
added simple adversary model

>>>>

We consider two types of adversaries: \begin{enumerate*} \item an honest-but-curious adversary
of up to national scale representing a government that can observe any
messages sent, and \item a malicious adversary that can control a
minority of 
equipment such as participants' or witnesses' smartphones or servers
used for the ledger such as miners for a blockchain. \end{enumerate*}
